Code Overflow: \\ An empirical study of online code reuse

### 2016-09-01 latex/stackoverflow.tex
Latest update

% This is LLNCS.DOC the documentation file of
% the LaTeX2e class from Springer-Verlag
% for Lecture Notes in Computer Science, version 2.4
%\documentclass{llncs}
\documentclass{IEEEtran}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{listings}  
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{float}
\usepackage{array}
\usepackage{ragged2e}
\newcolumntype{P}[1]{>{\RaggedRight\hspace{0pt}}p{#1}}

@@

\section*{Raw statistics}
The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stackoverflow fragments (Java accepted answers) and 63 open-source projects in Qualitas dataset is presented below. There are 2 tools selected: Simian and NiCad. They are configured using three different settings: default settings, settings from FSE'13 paper, and settings from CloPlag experiment. Full Simian's parameter names can be found from the footnote\footnote{Simian's parameters: iChar = ignoreCharacters, iCurlB = ignoreCurlyBraces, iId = ignoreIdentifiers, iIdC = ignoreIdentifierCase, iMod = ignoreModifiers \newline iStrC = ignoreStringCase, iStr = ignoreStrings, iSbtNm = ignoreSubtypeNames, bSqBrck=balanceSquareBrackets}.

@@

%\begin{table*}[h]
%	\centering
%	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (44 new + 19 old Qualitas projects)}
%	\label{t_simian_raw_results}
%	\resizebox{\columnwidth}{!}{%
%	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}

@@

%		\multirow{4}{*}{Statistics} 
%		& \multicolumn{4}{c|}{Simian Default settings} 
%		& \multicolumn{4}{c|}{Simian FSE'13 settings} 
%		& \multicolumn{4}{c|}{NiCad Default settings} 
%		& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
%		& \multicolumn{4}{c|}{threshold=6} 
%		& \multicolumn{4}{c|}{threshold=5} 
%		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
%		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
%		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
%		& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
%		& \multicolumn{4}{c|}{rename=none,abstract=none} 
%		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
%		% \hline
%		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
%		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
%		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
%		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
%		%Removed & 11 	& -- 	& -- 	& -- 	& 0 & -- & -- & -- \\ %& 11 & -- & -- & -- \\
%		Total 	& 789 	& 61,164 & -- 	& -- 	&  170 	& 11,915,544 & -- 	& --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
%		Mean 	& -- 	& 78 	& 7.32 	& 0.26 	& -- 	& 70,091 	& 4.76 	& 0.29 \\ % & -- & 9,356 & 4.74 & 0.26 \\
%		Std Dev. & -- 	& 208 	& 2.71 	& 0.21 	& -- 	& 703,788 	& 0.89 	& 0.19 \\ % & -- & 96,038	& 0.99 & 0.18 \\
%		Max 	& -- 	& 1,300 & 49 	& 0.94 	& -- 	& 9,065,774 & 9		& 0.83 \\ % & -- & 7,837,204 & 28 & 0.94 \\
%		Min 	& -- 	& 1 	& 5 	& 0.01 	& -- 	& 1 		& 4 	& 0.01 \\ % & -- & 1 & 4 & 0.002 \\
%		Median 	& -- 	& 2 	& 7 	& 0.20 	& -- 	& 17 		& 5 	& 0.26 \\ % & -- & 27 & 4 & 0.22 \\
%		Mode 	& -- 	& 1 	& 7 	& 0.33 	& -- 	& 1 		& 4 	& 0.33 \\ % & -- & 1 & 4 & 0.50 \\
%	\end{tabular} %
%}
%\end{table*}

@@

%\begin{table*}[h]
%	\centering
%	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (only 44 new Qualitas projects)}
%	\label{t_simian_raw_results}
%	\resizebox{\columnwidth}{!}{%
%		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
%			\multirow{4}{*}{Statistics} 
%			& \multicolumn{4}{c|}{Simian Default settings} 
%			& \multicolumn{4}{c|}{Simian FSE'13 settings} 
%			& \multicolumn{4}{c|}{NiCad Default settings} 
%			& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
%			& \multicolumn{4}{c|}{threshold=6} 
%			& \multicolumn{4}{c|}{threshold=5} 
%			& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
%			& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
%			& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
%			& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
%			& \multicolumn{4}{c|}{rename=none,abstract=none} 
%			& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
%			% \hline
%			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
%			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
%			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
%			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
%			%Removed & 11 	& -- 	& -- 	& -- 	& 0 & -- & -- & -- \\ %& 11 & -- & -- & -- \\
%			Total 	& 736 	& 60,678 & -- 	& -- 	&  166 	& 10,273,534 & -- 	& --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
%			Mean 	& -- 	& 82 	& 7.26 	& 0.26 	& -- 	& 61,889 	& 4.77 	& 0.28 \\ % & -- & 9,356 & 4.74 & 0.26 \\
%			Std Dev. & -- 	& 214 	& 2.24 	& 0.21 	& -- 	& 607,074 	& 0.89 	& 0.18 \\ % & -- & 96,038	& 0.99 & 0.18 \\
%			Max 	& -- 	& 1,298 & 32 	& 0.94 	& -- 	& 7,720,970 & 9		& 0.83 \\ % & -- & 7,837,204 & 28 & 0.94 \\
%			Min 	& -- 	& 1 	& 5 	& 0.01 	& -- 	& 1 		& 4 	& 0.01 \\ % & -- & 1 & 4 & 0.002 \\
%			Median 	& -- 	& 2 	& 7 	& 0.20 	& -- 	& 16.5 		& 5 	& 0.26 \\ % & -- & 27 & 4 & 0.22 \\
%			Mode 	& -- 	& 1 	& 7 	& 0.33 	& -- 	& 1 		& 4 	& 0.33 \\ % & -- & 1 & 4 & 0.50 \\
%		\end{tabular} %
%	}
%\end{table*}

@@

\section*{Agreed Clone Pairs}
The investigation of the clone pairs using Bellon's \textit{good-match(p)} and \textit{ok-match(p)} criteria are listed in  Table \ref{t_agreed_good_clone_pairs} and Table \ref{t_agreed_ok_clone_pairs}. We use the threshold \textit{p} of 0.7 for both \textit{good-match} and \textit{ok-match}. Visualisation of \textit{good-match} common clone pairs between sets of parameter settings can be seen from Figure \ref{fig:venn4_pairs}. There are 14 \textit{good-match} pairs. The \textit{ok-match} subsumes the \textit{good-match} resulting in totally 528 common clone pairs.

However, for the 2 NiCad settings, we found some renaming and clustering errors which resulted in fewer projects having clone reports. For NiCad default settings, 6 projects had clustering failed errors: \textit{cayenne,checkstyle, db-derby, geotools, hibernate, iReport}. For NiCad FSE13 settings, 4 projects had renaming failed errors: \textit{Vuze, aspectj, eXoPortal, hibernate} and 13 projects had clustering failed errors: \textit{ArgoUML, castor, cayenne, checkstyle, db-derby, drjava, ganttproject, geotools, iReport, ivatagroupware, jasperreports, jboss, jchempaint} as depicted in Table \ref{tab:projects_missing}. So these projects are also missing from agreed clone pairs.

\begin{table}[H]
	\centering
	\caption{Qualitas projects successfully analysed by Simian and NiCad}
	\label{tab:projects_missing}
	\begin{tabular}{r|r|r|r}
		\hline
		Simian$_{df}$ & NiCad$_{df}$ & Simian$_{fse13}$ & NiCad$_{fse13}$ \\ \hline
		63	& 57 & 63 & 46 \\
		\hline
		& \textit{6 clustering failed} &  & \textit{13 clustering failed} \\
		\hline
		& cayenne   &	& cayenne \\
		& checkstyle &  & checkstyle \\
		& db-derby 	& & db-derby \\
		& geotools 	& & geotools \\
		& iReport 	& & iReport \\
		& hibernate & & ArgoUML \\
		&			& & castor \\
		&			& & drjava \\
		&			& & ganttproject \\
		&			& & ivatagroupware \\
		&			& & jasperreports \\
		&			& & jboss \\
		&			& & jchempaint \\
		\hline
		& \textit{renaming failed} & &  \textit{4 renaming failed} \\
		\hline
		&			& & Vuze \\
		&			& & aspectj \\
		&			& & eXoPortal \\
		&			& &  hibernate \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{1,415 agreed good-match(0.7) cloned pairs between Simian and Nicad (1,406 are unique)}
	\label{t_agreed_good_clone_pairs}
	\begin{tabular}{l|r|r}
		\hline
		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		NiCad$_{\mathrm{\textit{default}}}$ & 9 & 6 \\ %      & 709             \\
		NiCad$_{\mathrm{\textit{fse13}}}$   & 12 & 1388 \\ % & 4680            \\
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

%\begin{table}[H]
%	\centering
%	\caption{Duplicated agreed \textit{good}-pairs between pairs of Simian and NiCad settings}
%	\label{t_dup_agreed_good_clone_pairs}
%	\begin{tabular}{l|r|r|r|r}
%		\hline
%		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
%		\hline
%		$S_dN_d$ & 9 &    &   &      \\%      & 709             \\
%		$S_dN_f$ & 9 & 12 &   &      \\ % & 4680            \\
%		$S_fN_d$ & 0 & 0  & 6 &      \\
%		$S_fN_f$ & 0 & 0  & 0 & 1388 \\	
%		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
%		\hline
%	\end{tabular}
%\end{table}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\linewidth]{venn4_pairs_good}
	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion}
	\label{fig:venn4_pairs}
\end{figure}

\begin{table}[H]
	\centering
	\caption{11,165 agreed \textit{ok}-match(0.7) cloned pairs between Simian and Nicad (10,879 are different, 286 are duplicates). They contain all \textit{good}-match pairs}
	\label{t_agreed_ok_clone_pairs}
	\begin{tabular}{l|r|r}
		\hline
		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		NiCad$_{\mathrm{\textit{default}}}$ & 481 & 60 \\%      & 709             \\
		NiCad$_{\mathrm{\textit{fse13}}}$   & 418 & 10,206 \\ % & 4680            \\
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Duplicated agreed \textit{ok}-pairs between Simian and NiCad settings (10,879 are different, 286 are duplicates)}
	\label{t_dup_agreed_ok_clone_pairs}
	\begin{tabular}{l|r|r|r|r|r}
		\hline
		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ & Total \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		$S_dN_d$ & 214 	& 267 	& 0		& 0 		& 481 \\
		$S_dN_f$ & 267 	& 150 	& 0 	& 1 		& 418 \\ 
		$S_fN_d$ & 0 	& 0 	& 42 	& 18  		& 60 \\
		$S_fN_f$ & 0 	& 1 	& 18 	& 10,187 	& 10,206 \\	
		\hline
		Total 	 & 481  & 418	& 60	& 10,206	& 11,165 \\
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\linewidth]{venn4_pairs_ok}
	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion}
	\label{fig:venn4_pairs}
\end{figure}

>>>>

% This is LLNCS.DOC the documentation file of
% the LaTeX2e class from Springer-Verlag
% for Lecture Notes in Computer Science, version 2.4
%\documentclass{llncs}
\documentclass{IEEEtran}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{listings}  
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{float}
\usepackage{array}
\usepackage{ragged2e}
\newcolumntype{P}[1]{>{\RaggedRight\hspace{0pt}}p{#1}}

@@

\section*{Raw statistics}
The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stackoverflow fragments (Java accepted answers) and 63 open-source projects in Qualitas dataset is presented below. There are 2 tools selected: Simian and NiCad. They are configured using two different settings: default settings, and settings from another study \cite{Wang2013}. Full Simian's parameter names can be found from the footnote\footnote{Simian's parameters: iChar = ignoreCharacters, iCurlB = ignoreCurlyBraces, iId = ignoreIdentifiers, iIdC = ignoreIdentifierCase, iMod = ignoreModifiers \newline iStrC = ignoreStringCase, iStr = ignoreStrings, iSbtNm = ignoreSubtypeNames, bSqBrck=balanceSquareBrackets}.

@@

\begin{table*}[h]
	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (44 new + 19 old Qualitas projects)}
	\label{t_simian_raw_results}
	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
		\multirow{4}{*}{Statistics} 
		& \multicolumn{4}{c|}{Simian Default settings} 
		& \multicolumn{4}{c|}{Simian FSE'13 settings} 
		& \multicolumn{4}{c|}{NiCad Default settings} 
		& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
		& \multicolumn{4}{c|}{threshold=6} 
		& \multicolumn{4}{c|}{threshold=5} 
		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
		& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
		& \multicolumn{4}{c|}{rename=none,abstract=none} 
		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\

@@

		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
		Total 	& 792 & 61,268 & -- & -- 	& 1,229 & 25,725,857 & -- & -- & 1,141 	& 666,140 & -- 	& -- 	&  12,400 	& 615,263,639 & -- 	& --  \\ 
		Mean 	& -- & 78 & 7.31 & 0.26 	& -- & 20,932 & 4.86 & 0.28 & -- 	& 584 	& 9.49 	& 0.25 	& -- 	& 49,618 	& 5.25 	& 0.20 \\ 
		Std Dev. & -- & 208 & 2.70 & 0.21 	& -- & 382,015 & 1.30 & 0.19 & -- 	& 1,488 & 3.11 	& 0.18 	& -- 	& 62,659 	& 2.80 	& 0.16 \\ 
		Max 	& -- & 1,300 & 49.00 & 0.94 & -- & 13,202,807 & 21.00 & 0.92 & -- 	& 10,980 & 39.00 	& 0.84 	& -- 	& 1,319,242 & 250.00	& 0.96 \\
		Min 	& -- & 1 & 5.00 & 0.01 		& -- & 1 & 4.00 & 0.12 & -- 	& 1 	& 7.00 	& 0.02 	& -- 	& 1 		& 2.00 	& 0.01 \\ 
		Median 	& -- & 2 & 7.00 & 0.20 		& -- & 21 & 5.00 & 0.25 & -- 	& 25 	& 8.00 	& 0.19 	& -- 	& 52,329 	& 5.00 	& 0.16 \\ 
		Mode 	& -- & 1 & 7.00 & 0.33 		& -- & 1 & 4.00 & 0.50 & -- 	& 1 	& 8.00 	& 0.67 	& -- 	& 1 		& 4.00 	& 0.33 \\ 
\end{table*}

@@

\begin{table*}[h]
	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (only 44 new Qualitas projects)}
	\label{t_simian_raw_results}
		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
			\multirow{4}{*}{Statistics} 
			& \multicolumn{4}{c|}{Simian Default settings} 
			& \multicolumn{4}{c|}{Simian FSE'13 settings} 
			& \multicolumn{4}{c|}{NiCad Default settings} 
			& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
			& \multicolumn{4}{c|}{threshold=6} 
			& \multicolumn{4}{c|}{threshold=5} 
			& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
			& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
			& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
			& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
			& \multicolumn{4}{c|}{rename=none,abstract=none} 
			& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  
			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
			Total 	& 707 	& 60,536 & -- 	& -- 	&  1,205 & 22,797,190 & -- 	& --  & 1,068 & 648,165 & -- & -- & 10,231 & 573,438,528 & -- & -- \\ 
			Mean 	& -- 	& 86 	& 7.37 	& 0.26 	& -- 	& 18,919 	& 4.85 	& 0.28 & -- & 607 & 9.39 & 0.25 & -- & 47663 & 5.22 & 0.20 \\
			Std Dev. & -- 	& 217 	& 2.22 	& 0.21 	& -- 	& 326,588 	& 1.31 	& 0.19 & -- & 1,499 & 2.98 & 1.81 & -- & 58,833 & 2.77 & 0.15 \\
			Max 	& -- 	& 1,298 & 32.00 & 0.94 	& -- 	& 11,127,286 & 21.00 & 0.92 & -- & 10,550 & 36.00 & 0.84 & -- & 1,246,598 & 250 & 0.96 \\
			Min 	& -- 	& 1 	& 5.00 	& 0.01 	& -- 	& 1 		& 4.00 	& 0.02 & -- & 1 & 7 & 0.02 & -- & 1 & 2.00 & 0.01\\
			Median 	& -- 	& 2 	& 7.00 	& 0.21 	& -- 	& 20		& 5.00 	& 0.25 & -- & 33 & 8 & 0.19 & -- & 52,077 & 5.00 & 0.15 \\
			Mode 	& -- 	& 1 	& 7.00 	& 0.25 	& -- 	& 1 		& 4.00 	& 0.50 & -- & 1 & 8 & 0.67 & -- & 1 & 4.00 & 0.33 \\
\end{table*}

@@

\section*{Agreed Clone Pairs}

The agreed clone pairs using Bellon's \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria are listed in  Table \ref{t_agreed_good_clone_pairs}. We use the threshold of 0.7 for both \textit{good}-match and \textit{ok}-match. Visualisation of \textit{good}-match common clone pairs between sets of parameter settings can be seen from Figure \ref{fig:venn4_orig_good}. There are 1,406 unique \textit{good}-match pairs. The \textit{ok}-match subsumes the \textit{good}-match resulting in totally 10,879 common clone pairs (Figure \ref{fig:venn4_orig_ok}).

However, for NiCad's settings, we found a few renaming and clustering errors which resulted in fewer projects with clone reports. For NiCad default settings (NiCad$_{\textrm{\textit{df}}}$), 6 projects had clustering failed errors. For NiCad FSE13 settings (NiCad$_{\textrm{\textit{fse13}}}$), 4 projects had renaming failed errors and 13 projects had clustering failed errors as depicted in Table \ref{tab:projects_missing}. So these projects are also missing from agreed clone pairs. \FIXME{Report the errors.}

We are interested in discovering reused code in the latest versions of Qualitas projects. So, we downloaded the newest release of each project and found 44 of them having newer updates. Then, we reran the experiment again on these 44 projects. Several projects triggered NiCad problem of clustering and renaming again as listed in Table \ref{tab:projects_missing}. The agreed clone pairs using Bellon's \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria of this new dataset are also listed in Table \ref{t_agreed_good_clone_pairs}.

\begin{table}[H]
	\centering
	\caption{No.~of projects in Qualitas Original~(Qualitas-\textit{O}) and New (Qualitas-\textit{N}) successfully analysed by Simian and NiCad}
	\label{tab:projects_missing}
	\begin{tabular}{r|r|r|r|r|r|r|r}
		\hline
		\multicolumn{4}{c|}{Qualitas-\textit{O}} & \multicolumn{4}{c}{Qualitas-\textit{N}} \\
		\hline
		Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{fse13}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{fse13}}}$ & Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{fse13}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{fse13}}}$ \\ \hline
		63	& 63 & 57 & 46 & 44 & 44 & 40 & 34 \\
		\hline
		& & \textit{6 clustering failed} & \textit{13 clustering failed} & & & \textit{4 clustering failed} & \textit{6 clustering failed} \\
		& & cayenne   & cayenne 	& & & jboss (wildfly) & ArgoUML \\
		& & checkstyle & checkstyle & & & hadoop & checkstyle \\
		& & db-derby 	& db-derby 	& & & db-derby & db-derby \\
		& & geotools 	& geotools  & & & hibernate & cayenne \\
		& & iReport 	& iReport   & & & & jena \\
		& & hibernate & ArgoUML 	& & & & geotools \\
		& &			& castor 		& & & & \\
		& &			& drjava 		& & & & \\
		& &			& ganttproject 	& & & & \\
		& &			& ivatagroupware & & & &  \\
		& &			& jasperreports & & & & \\
		& &			& jboss 		& & & & \\
		& &			& jchempaint 	& & & & \\
		\hline
		& 			& &  \textit{4 renaming failed} & & & & \\
		&			& & Vuze 		& & & & Vuze \\
		&			& & aspectj 	& & & & hadoop \\
		&			& & eXoPortal 	& & & & jboss (wildfly) \\
		&			& &  hibernate 	& & & & hibernate \\
		\hline
	\end{tabular}
\end{table}

%\begin{table}[H]
%	\centering
%	\caption{Qualitas projects (2016-08-16) successfully analysed by Simian and NiCad}
%	\label{tab:projects_missing_new}
%	\begin{tabular}{r|r|r|r}
%		\hline
%		Simian$_{df}$ & NiCad$_{df}$ & Simian$_{fse13}$ & NiCad$_{fse13}$ \\ \hline
%		44	& 40 & 44 & 34 \\
%		\hline
%		& \textit{4 clustering failed} &  & \textit{6 clustering failed} \\
%		\hline
%		& jboss (wildfly) &	& ArgoUML \\
%		& db-derby 	&  &  db-derby \\
%		& hadoop 	& &  checkstyle \\
%		& hibernate & &  cayenne \\
%		&  			& &  geotools \\
%		&  			& &  jena \\
%		\hline
%		& \textit{no renaming failed} & &  \textit{4 renaming failed} \\
%		\hline
%		&			& & Vuze \\
%		&			& & hadoop \\
%		&			& & hibernate \\
%		&			& & jboss (wildfly) \\
%		\hline
%	\end{tabular}
%\end{table}

\begin{table}[H]
	\centering
	\caption{Distribution of clone pairs reported based on \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria}
	\label{t_agreed_good_clone_pairs}
	\begin{tabular}{l|l|r|r|r|r}
		\hline
		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c|}{Qualitas-\textit{O}} & \multicolumn{2}{c}{Qualitas-\textit{N}} \\
		\hline
		Simian & NiCad & \textit{good}-match & \textit{ok}-match & \textit{good}-match & \textit{ok}-match \\
		%\hline
		%Settings & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		\textit{default} & \textit{default} & 9 	& 481 	& 0 & 6,640 \\ 
		\textit{default} & \textit{fse13} 	& 12 	& 418 	& 0 & 416 \\ 
		\textit{fse13} 	& \textit{default} 	& 6 	& 60 	& 0 & 23 \\
		\textit{fse13} 	& \textit{fse13} 	& 1,388 & 10,206 & 1,170 & 6,690 \\ 
		\hline
		\multicolumn{2}{l|}{Total} & 1,415 & 11,165 & 1,170 & 13,386 \\
		\multicolumn{2}{l|}{Total (unique)} & 1,406 & 10,879 & 1,170 & 10,879 \\
		\hline
	\end{tabular}
\end{table}

%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.5\linewidth]{venn4_pairs_good}
%	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion}
%	\label{fig:venn4_pairs_good}
%\end{figure}

%\begin{table}[H]
%	\centering
%	\caption{11,165 agreed \textit{ok}-match(0.7) cloned pairs between Simian and Nicad (10,879 are different, 286 are duplicates). They contain all \textit{good}-match pairs}
%	\label{t_agreed_ok_clone_pairs}
%	\begin{tabular}{l|r|r}
%		\hline
%		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
%		\hline
%		NiCad$_{\mathrm{\textit{default}}}$ & 481 & 60 \\%      & 709             \\
%		NiCad$_{\mathrm{\textit{fse13}}}$   & 418 & 10,206 \\ % & 4680            \\
%		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
%		\hline
%	\end{tabular}
%\end{table}

\begin{figure}
	\centering
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{venn4_pairs_good}
		\captionof{figure}{Qualitas-\textit{O} \textit{good}-match(0.7) pairs}
		\label{fig:venn4_orig_good}
	\end{minipage}%
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{venn4_pairs_ok}
		\captionof{figure}{Qualitas-\textit{O} \textit{ok}-match(0.7) pairs}
		\label{fig:venn4_orig_ok}
	\end{minipage}
\end{figure}

%\begin{table}[H]
%	\centering
%	\caption{Duplicated agreed \textit{ok}-pairs between Simian and NiCad settings (10,879 are different, 286 are duplicates)}
%	\label{t_dup_agreed_ok_clone_pairs}
%	\begin{tabular}{l|r|r|r|r|r}
%		\hline
%		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ & Total \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
%		\hline
%		$S_dN_d$ & 214 	& 267 	& 0		& 0 		& 481 \\
%		$S_dN_f$ & 267 	& 150 	& 0 	& 1 		& 418 \\ 
%		$S_fN_d$ & 0 	& 0 	& 42 	& 18  		& 60 \\
%		$S_fN_f$ & 0 	& 1 	& 18 	& 10,187 	& 10,206 \\	
%		\hline
%		Total 	 & 481  & 418	& 60	& 10,206	& 11,165 \\
%		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
%		\hline
%	\end{tabular}
%\end{table}

%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.5\linewidth]{venn4_pairs_ok}
%	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion}
%	\label{fig:venn4_pairs}
%\end{figure}

%The statistics of the results from Simian and NiCad are shown in Table \ref{t_agreed_good_clone_pairs_new}, \ref{t_agreed_ok_clone_pairs_new}, and Figure \ref{fig:venn4_pairs_good_new}, and \ref{fig:venn4_pairs_ok_new}.
%
%\begin{table}[H]
%	\centering
%	\caption{1,170 agreed good-match(0.7) cloned pairs between Simian and Nicad (1,170 are unique)}
%	\label{t_agreed_good_clone_pairs_new}
%	\begin{tabular}{l|r|r}
%		\hline
%		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\
%		\hline
%		NiCad$_{\mathrm{\textit{default}}}$ & 0 & 0 \\ 
%		NiCad$_{\mathrm{\textit{fse13}}}$   & 0 & 1,170 \\ 
%		\hline
%	\end{tabular}
%\end{table}
